SVG: The Paper

### 2022-04-20 Analysis/index.Rmd
init sel model fits

---
title: 'SVG: The Paper'
author: "Alasdair Clarke, Amelia Hunt &  Anna Hughes"
date: "13/04/2022"
output:
  tufte::tufte_html:
    toc: TRUE
    number_sections: true
---

@@

obs_fits_x <- pmap_dfc(filter(am,  dim == "x") %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
  mutate(z = z) %>%
  pivot_longer(-z, names_to = "observer", values_to = "v") %>%
  ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
  scale_x_continuous("x")

obs_fits_y <- pmap_dfc(filter(am,  dim == "y") %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
  mutate(z = z) %>%
  pivot_longer(-z, names_to = "observer", values_to = "v") %>%
  ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
  scale_x_continuous("y") + 
  coord_flip()

>>>>

---
title: 'SVG: The Paper'
author: "Alasdair Clarke, Amelia Hunt &  Anna Hughes"
date: "13/04/2022"
output:
  tufte::tufte_html:
    toc: TRUE
    number_sections: true
    fig_height: 4 
---

@@

obs_fits_x <- pmap_dfc(filter(am,  dim == "x") %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
  mutate(z = z) %>%
  pivot_longer(-z, names_to = "observer", values_to = "v") %>%
  ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
  scale_x_continuous("x") + scale_y_continuous("likelihood")

obs_fits_y <- pmap_dfc(filter(am,  dim == "y") %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
  mutate(z = z) %>%
  pivot_longer(-z, names_to = "observer", values_to = "v") %>%
  ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
  scale_x_continuous("y") + scale_y_continuous("likelihood")
